Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms} \footnote{Lecture is based upon the materials provided by MSB~\cite{msb_metodstod} and previous lectures written by Carina Bengtsson and Daniel Bosk}.

### 2019-04-02 msbframework/msbintro/msbintro.tex
Moved another slide.
Changed heading on one slide

@@

\begin{frame}{The security isn't stronger than the weakest link}{What is information security?}
  \begin{itemize}
    \item Strong password, written down on a post-it next to where it should be
      used.
    \item High grade lock on a regular glass door.
    \item The conditions must be there, in order to be able to work safely.
  \end{itemize}
\end{frame}

@@

\begin{frame}{Why protect the information?}{Non-mandatory}
  \enquote{Good for business}
  \begin{description}
    \item[Reputation:] Who will let a company handle their information, if the
      company is known for treating their data carelessly.
    \item[Financial:] Strong reputation is better for the economy, and the cost
      of dealing with security incidents will be less.
    \item[Internal efficiency:] No loss of information or disruptions in the
      work.
    \item[Quality:] This will hopefully lead to a increase in work quality.
  \end{description}
\end{frame}

>>>>

\begin{frame}{Why protect the information?}{What is information security?}
  \enquote{Good for business}
  \begin{description}
    \item[Reputation:] Who will let a company handle their information, if the
      company is known for treating their data carelessly.
    \item[Financial:] Strong reputation is better for the economy, and the cost
      of dealing with security incidents will be less.
    \item[Internal efficiency:] No loss of information or disruptions in the
      work.
    \item[Quality:] This will hopefully lead to a increase in work quality.
  \end{description}
\end{frame}

@@

\begin{frame}{Where should we implement it?}{What is information security?}
The security isn't stronger than the weakest link
  \begin{itemize}
    \item Strong password, written down on a post-it next to where it should be
      used.
    \item High grade lock on a regular glass door.
    \item The conditions must be there, in order to be able to work safely.
  \end{itemize}
\end{frame}

@@
